---
title: "Sim_pred"
author: "Wentao Zhan"
date: "2022/3/9"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=F, warning = FALSE, echo = TRUE)

library(tidyverse)
library(reshape2)
library(scoringutils)
```

```{r}
CI = function(data){
  n = nrow(data)
  coverage_NN = sum(data$Y<data$CI_U_NN & data$Y>data$CI_L_NN)/n
  coverage_NNGLS = sum(data$Y<data$CI_U_NNGLS & data$Y>data$CI_L_NNGLS)/n
  c('coverage_NN' = coverage_NN, 'coverage_NNGLS' = coverage_NNGLS)
}

PI = function(data){
  n = nrow(data)
  coverage_NN = sum(data$Y<data$PI_U_NN & data$Y>data$PI_L_NN)/n
  coverage_NNGLS = sum(data$Y<data$PI_U_NNGLS & data$Y>data$PI_L_NNGLS)/n
  c('coverage_NN' = coverage_NN, 'coverage_NNGLS' = coverage_NNGLS)
}

```

```{r}
data = read.csv('./round9.4/CI_sinprop08rep1000.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

data_plt = melt(data, id = 'x')

ggplot(data_plt, aes(x = x, y = value)) + 
  geom_line(aes(group = variable, color = variable))

CI(data)
```

```{r}
data = read.csv('./round9.4/CI_friedmanprop05rep100.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_friedmanprop05rep100sig10.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_sinprop05rep100.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)

x = read.csv('x.csv')[,-1]
plot(x = x, y = rowMeans(CI_table))
```

```{r}
data = read.csv('./round9.4/CI_sinprop05rep100sig10.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_linprop05rep100.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_linprop05rep1000.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_constprop05rep100.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
data = read.csv('./round9.4/CI_constprop05rep1000.csv')[-1]
data['x'] = read.csv('x.csv')[,-1]

size = table(data$index)[1]
rand = length(table(data$index))
CI_table = matrix(nrow = size, ncol = 2)
for(i in 1:size){
  data_temp = data[((1:rand)-1)*size + i, ]
  CI_table[i,] = CI(data_temp)
}

colMeans(CI_table)
```

```{r}
df = data.frame(date = '20230904', fx = rep(c('Friedman', 'Friedman', 'Sin', 'Sin', 
                                         'Linear', 'Linear', 'Const', 'Const'), each = 2),
               method = rep(c('NN', 'NNGLS'), 8), prop = 0.5, sigma = rep(c(1, 10), 8),
               coverage = c(0.740521, 0.830708, 0.958186, 0.991372, 
                            0.97691, 0.99655, 0.979907, 0.998698,
                            0.999557, 1.000000, NA, NA,
                            1, 1, NA, NA))

df
```

```{r}
df = readRDS('df.rds')
```

#20230904: Initial experiments
#20230911: First systematic experiment. Sample got reordered when subsample so that prop=0 does not give 0 coverage.
#20230913: Fixed subsampling-ordering issue (not able to reproduce)
#20230919: Fixed the ordering issue of I_B and F and added prediction interval
#20230922: Rerun prediction interval and use the fixed 0913 script for reproducibility check.

```{r}
date = '20231001'
for(sigma in c(1,10)){
  for(func in c('Sin', 'Friedman')){
    for(prop in 1){
      print(prop)
      data = read.csv(paste0('./', date, '/CI_', tolower(func), 'prop', as.character(prop*100),
                             'rep100sig', as.character(sigma), 'decor.csv'))[-1]
      data['x'] = read.csv('x.csv')[,-1]
      size = table(data$index)[1]
      rand = length(table(data$index))
      CI_table = matrix(nrow = size, ncol = 2)
      for(i in 1:size){
        data_temp = data[((1:rand)-1)*size + i, ]
        CI_table[i,] = CI(data_temp)
      }
    
    
      df_temp = x = data.frame(date = date, fx = func,
                   method = c('NN', 'NNGLS'), prop = prop, sigma = sigma,
                   coverage = colMeans(CI_table), resample = 'decor')
      df = rbind(df, df_temp)
    }
  }
}
```

```{r}
date = '20230919'
prop = 1
func = 'Friedman'
df_CI = data.frame(matrix(nrow = 0, ncol = 3))
colnames(df_CI) = c('NN', 'NNGLS', 'x')
for(sigma in c(1, 10)){
  print(sigma)
  data = read.csv(paste0('./', date, '/CI_', tolower(func), 'prop', as.character(prop*100),
                         'rep100sig', as.character(sigma), 'decor.csv'))[-1]
  data['x'] = read.csv('x.csv')[,-1]
  size = table(data$index)[1]
  rand = length(table(data$index))
  CI_table = matrix(nrow = size, ncol = 2)
  for(i in 1:size){
    data_temp = data[((1:rand)-1)*size + i, ]
    CI_table[i,] = CI(data_temp)
  }


  df_temp = data.frame(date = date, fx = func,
               method = c('NN', 'NNGLS'), prop = prop, sigma = sigma,
               coverage = colMeans(CI_table), resample = 'decor')
  df = rbind(df, df_temp)
}
```

```{r}
saveRDS(df, 'df.rds')
```

```{r}
df %>% filter(resample =='decor') %>% ggplot(aes(x = method, y = coverage)) +
  geom_boxplot() + facet_grid(fx ~ sigma)
```

```{r}
df %>% filter(date == '20230919'& fx == 'Friedman' & resample == 'subsample') %>%
  ggplot(aes(x = prop, y = coverage,
            group = method,
            colour = method)) + geom_point() + geom_line() + 
  geom_hline(yintercept=0.95, linetype='dashed', col = 'black') +
  facet_wrap(~sigma, labeller = label_both) +
  ggtitle('Coverage for Friedman function')
ggsave('Friedman-0919.png')
```

```{r}
df %>% filter(date == '20230921'& fx == 'Sin' & resample == 'subsample') %>%
  ggplot(aes(x = prop, y = coverage,
            group = method,
            colour = method)) + geom_point() + geom_line() + 
  geom_hline(yintercept=0.95, linetype='dashed', col = 'black') +
  facet_wrap(~sigma, labeller = label_both) +
  ggtitle('Coverage for Sin function')
ggsave('Sin-0921.png')
```

Sin coverage vs x.
```{r}
date = '20230921'
prop = 0.5
method = 'Sin'
resample = 'subsample'

df_CI = data.frame(matrix(nrow = 0, ncol = 4))
colnames(df_CI) = c('NN', 'NNGLS', 'x', 'sigma')
for(sigma in c(1, 10)){
  print(sigma)
  data = read.csv(paste0('./', date, '/CI_', tolower(method), 'prop', as.character(prop*100),
                         'rep100sig', as.character(sigma), resample, '.csv'))[-1]
  data['x'] = read.csv('x.csv')[,-1]
  size = table(data$index)[1]
  rand = length(table(data$index))
  CI_table = matrix(nrow = size, ncol = 2)
  for(i in 1:size){
    data_temp = data[((1:rand)-1)*size + i, ]
    CI_table[i,] = CI(data_temp)
  }
  
  df_CI_temp = data.frame(cbind(CI_table), read.csv('x.csv')[,-1])
  colnames(df_CI_temp) =  c('NN', 'NNGLS', 'x')
  df_CI_temp$sigma = sigma
  df_CI = rbind(df_CI, df_CI_temp)
}

df_CI_plt = melt(df_CI, id.vars = c('x', 'sigma'), 
                 variable.name = 'method', value.name = 'coverage')

df_CI_plt %>% ggplot(aes(x = x, y = coverage, group = method, color = method)) +
  geom_point(size = 0.5) + geom_hline(yintercept=0.95, linetype='dashed', col = 'black') +
  facet_wrap(~sigma, labeller = label_both) +
  theme(legend.text = element_text(size=18), legend.title = element_text(size=20),
        axis.text=element_text(size=15), axis.title=element_text(size=18),
        strip.text.x = element_text(size = 13), strip.text.y = element_text(size = 13))
+
  ggtitle(paste0(method, '-', resample)) 

ggsave(paste0(method, '-', resample, '-prop', as.character(as.integer(prop*100)), '.png'))
```
Friedman coverage vs x.
```{r}
date = '20230921'
prop = 0.5
method = 'Friedman'
resample = 'subsample'

df_CI = data.frame(matrix(nrow = 0, ncol = 3+5))
colnames(df_CI) = c('NN', 'NNGLS', paste0('x', 1:5), 'sigma')
for(sigma in c(1, 10)){
  print(sigma)
  data = read.csv(paste0('./', date, '/CI_', tolower(method), 'prop', as.character(prop*100),
                         'rep100sig', as.character(sigma), resample, '.csv'))[-1]
  size = table(data$index)[1]
  rand = length(table(data$index))
  CI_table = matrix(nrow = size, ncol = 2)
  for(i in 1:size){
    data_temp = data[((1:rand)-1)*size + i, ]
    CI_table[i,] = CI(data_temp)
  }
  
  df_CI_temp = data.frame(cbind(CI_table), read.csv('x5.csv')[,-1])
  colnames(df_CI_temp) =  c('NN', 'NNGLS', paste0('x', 1:5))
  df_CI_temp$sigma = sigma
  df_CI = rbind(df_CI, df_CI_temp)
}

df_CI_plt = df_CI %>% 
  melt(id.vars = c(paste0('x', 1:5), 'sigma'), 
                           variable.name = 'method', value.name = 'coverage') %>%
  melt(id.vars = c('sigma', 'method', 'coverage'), 
       variable.name = 'covariate', value.name = 'x')

df_CI_plt %>% ggplot(aes(x = x, y = coverage, group = method, color = method)) +
  geom_point(size = 0.5, alpha = 0.5) + geom_hline(yintercept=0.95, linetype='dashed', col = 'black') +
  facet_grid(covariate ~ sigma, labeller = label_both) +
  ggtitle(paste0(method, '-', resample)) 

ggsave(paste0(method, '-', resample, '-prop', as.character(as.integer(prop*100)), '.png'), height = 20, width = 10)
```
```{r}
date = '20230919'
for(sigma in c(1,10)){
  for(func in c('Sin', 'Friedman')){
    for(prop in c(1:10)/10){
      print(prop)
      data = read.csv(paste0('./', date, '/CI_', tolower(func), 'prop', as.character(prop*100),
                             'rep100sig', as.character(sigma), 'subsample.csv'))[-1]
      data['x'] = read.csv('x.csv')[,-1]
      size = table(data$index)[1]
      rand = length(table(data$index))
      
      process_fun = function(x){
        size = nrow(x)
        c(NN = mean(interval_score(x$Y, x$CI_L_NN, x$CI_U_NN, rep(95, size))),
          NNGLS = mean(interval_score(x$Y, x$CI_L_NNGLS, x$CI_U_NNGLS, rep(95, size))))
      }
      score_table = sapply(split(data, data$index), process_fun)
    
      df_temp = x = data.frame(date = date, fx = func,
                   method = c('NN', 'NNGLS'), prop = prop, sigma = sigma,
                   score = rowMeans(score_table), resample = 'subsample')
      df_score = rbind(df_score, df_temp)
    }
  }
}
```

```{r}
date = '20230921'
prop = 1
func = 'Sin'
df_temp = NULL
for(sigma in c(1, 10)){
  print(sigma)
  data = read.csv(paste0('./', date, '/CI_', tolower(func), 'prop', as.character(prop*100),
                         'rep100sig', as.character(sigma), 'decor.csv'))[-1]
  data['x'] = read.csv('x.csv')[,-1]
  size = table(data$index)[1]
  rand = length(table(data$index))
  process_fun = function(x){
        size = nrow(x)
        c(NN = mean(interval_score(x$Y, x$CI_L_NN, x$CI_U_NN, rep(95, size))),
          NNGLS = mean(interval_score(x$Y, x$CI_L_NNGLS, x$CI_U_NNGLS, rep(95, size))))
  }
  score_table = sapply(split(data, data$index), process_fun)

  df_temp = x = data.frame(date = date, fx = func,
               method = c('NN', 'NNGLS'), prop = prop, sigma = sigma,
               score = rowMeans(score_table), resample = 'decor')
  df_score = rbind(df_score, df_temp)
}
```
```{r}
df_score %>% filter(date == '20230921'& fx == 'Friedman' & resample == 'subsample') %>%
  ggplot(aes(x = prop, y = score,
            group = method,
            colour = method)) + geom_point() + geom_line() + 
  facet_wrap(~sigma, labeller = label_both) +
  ggtitle('Interval score for Friedman function')
ggsave('Score-Friedman-0921.png')
```

```{r}
df_score %>% filter(date == '20230921'& fx == 'Sin' & resample == 'subsample') %>%
  ggplot(aes(x = prop, y = score,
            group = method,
            colour = method)) + geom_point() + geom_line() + 
  facet_wrap(~sigma, labeller = label_both) +
  ggtitle('Interval score for Friedman function')
ggsave('Score-Sin-0921.png')
```



```{r}
df_PI = readRDS('df_PI.rds')

df_PI
```

```{r}
date = '20230921'
func = 'Sin'
for(sigma in c(1, 10)){
  print(sigma)
  data = read.csv(paste0('./', date, '/PI_', tolower(func), 'sig', as.character(sigma), '.csv'))[-1]
  data['x'] = read.csv('x.csv')[,-1]
  size = table(data$index)[1]
  rand = length(table(data$index))
  PI_table = matrix(nrow = size, ncol = 2)
  for(i in 1:size){
    data_temp = data[((1:rand)-1)*size + i, ]
    PI_table[i,] = PI(data_temp)
  }


  df_temp = data.frame(date = date, fx = func,
                       method = c('NN', 'NNGLS'), prop = prop, sigma = sigma,
                       coverage = colMeans(PI_table), resample = 'subsample')
  df_PI = rbind(df_PI, df_temp)
}

```

```{r}
saveRDS(df_PI, 'df_PI.rds')
```

```{r}
type = 'CI_cov'
func = 'friedman'
p = 5

date = '20231102'
sigma_vec = c(1, 5)
phi_vec = c(1, 3, 6)
tau_vec = as.character(c(1, 25))
cols = c('tau', 'Method', 'MISE')

path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
              '/', date, '/')

names = c('NN', 'NNGLS')
names_alt =  c('NN', 'NNGLS')


data = data.frame(matrix(ncol = 5))
colnames(data) = c('variable', 'value', 'sigma', 'phi', 'tau')
#print(list.files('./new_data'))
for(i in 1:length(sigma_vec)){
  for(j in 1:length(phi_vec)){
    for(k in 1:length(tau_vec)){
      filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', type, '.csv'), collapse = '')
      #print(!(filename %in% list.files('./new_data')))
      if(!(filename %in% list.files(path))){next}
      df_temp = read.csv(paste0(path, filename))[, names]
      colnames(df_temp) = names_alt
      df_temp = melt(df_temp)
      df_temp$sigma = sigma_vec[i]
      df_temp$phi = round(phi_vec[j]/sqrt(2),1)
      df_temp$tau = tau_vec[k]
      
      data = rbind(data, df_temp)
    }
  }
  
}
data = data[-1,]
data = data[complete.cases(data),]
data_plt = data %>% group_by(sigma, phi, tau, variable) %>% summarise(value = mean(value))
colnames(data_plt)[4:5] = c('Method', 'value') 
ggplot(data_plt, aes(x = tau, y = value)) + 
  geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
  #scale_fill_manual(values=group.colors[names_alt]) +
  xlab("tau %") +
  facet_grid(sigma ~ phi, scales = 'free', labeller = label_both) +
  theme(legend.text = element_text(size=15), legend.title = element_text(size=20),
        axis.text=element_text(size=12), axis.title=element_text(size=15),
        strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))

grid.arrange(p[[1]], p[[2]], nrow=2)
```

#20231028: Try confidence intervals using updated code(sparse), for oracle, decor, subsample case.
#20231101: Added subsample for Sparse case and decor for non-sparse case, use NNGLS estimation for decor, chol.
#20231102: Use symmetry to improve the efficiency, no chol
#20231103: corrected the sign of residual
#20231105: no longer using oracle BF matrix, sparse design having problem, changing to larger phi, sparseB class in 02, keep non-sparse version only afterwards
#20231105-2: corredted sparse class issue, use phi = 3, 6, corrected NN implementation afterwards, implemented parametric bootstrap as oracle implementation.
#20231108: corredted NN implementation

```{r}
require(gridExtra)
resample = 'decor'
func = 'sin'
#sparse = 'NS'
#resample = 'subsample'
p = 1
date = '20231114'
n = 0
p_list = list()
for(type in c('cali_CI_cov', 'cali_CI_score')){
  for(sparse in c('NS')){
    n = n+1
    sigma_vec = c(1, 5)
    phi_vec = c(1, 3, 6)
    tau_vec = as.character(c(1, 25))
    cols = c('tau', 'Method', 'MISE')
    
    path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
                  '/', date, '/')
    
    names = c('NN', 'NNGLS')
    names_alt =  c('NN-nonspatial', 'NN-GLS')
    
    
    data = data.frame(matrix(ncol = 5))
    colnames(data) = c('variable', 'value', 'sigma', 'phi', 'tau')
    #print(list.files('./new_data'))
    for(i in 1:length(sigma_vec)){
      for(j in 1:length(phi_vec)){
        for(k in 1:length(tau_vec)){
          filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', sparse, '_', type, '.csv'), collapse = '')
          #print(!(filename %in% list.files('./new_data')))
          if(!(filename %in% list.files(path))){next}
          df_temp = read.csv(paste0(path, filename))[, names]
          colnames(df_temp) = names_alt
          df_temp = melt(df_temp)
          df_temp$sigma = sigma_vec[i]
          df_temp$phi = round(phi_vec[j]/sqrt(2),1)
          df_temp$tau = tau_vec[k]
          
          data = rbind(data, df_temp)
        }
      }
      
    }
    data = data[-1,]
    data = data[complete.cases(data),]
    data_plt = data %>% group_by(sigma, phi, tau, variable) %>% summarise(value = mean(value))
    colnames(data_plt)[4:5] = c('Method', 'value') 
    data_plt$Method = factor(data_plt$Method, levels = names_alt)
    p_list[[n]] = ggplot(data_plt, aes(x = tau, y = value)) + #geom_hline(yintercept=0.95) +
              geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
              scale_fill_manual(values=group.colors[names_alt]) +
              xlab("tau %") +
              facet_grid(sigma ~ phi, scales = 'free', labeller = label_both) +
              theme(legend.text = element_text(size=15), legend.title = element_text(size=20),
                    axis.text=element_text(size=12), axis.title=element_text(size=15),
                    strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))
  }
}

p_list[[1]] + geom_hline(yintercept=0.95) + ylab('Coverage')
ggsave(paste0(func, '_coverage.png'), width = 10, height = 6)
p_list[[2]] + ylab('Interval score')
ggsave(paste0(func, '_score.png'), width = 10, height = 6)
#p_list[[3]]
#p_list[[4]]
```

```{r}
require(gridExtra)
resample = 'decor'
func = 'sin'
#sparse = 'NS'
#resample = 'subsample'
p = 1
date = '20231109'
n = 0
p_list = list()
for(type in c('msft_CI_cov', 'msft_CI_score')){
  for(sparse in c('NS')){
    n = n+1
    sigma_sq_vec = c(1, 5)
    phi_vec = c(1, 3, 6)
    tau_vec = as.character(c(1, 25))
    cols = c('tau', 'Method', 'MISE')
    
    path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
                  '/', date, '/')
    
    names = c('NN', 'NNGLS')
    names_alt =  c('NN-nonspatial', 'NN-GLS')
    
    
    data = data.frame(matrix(ncol = 5))
    colnames(data) = c('variable', 'value', 'sigma_sq', 'phi', 'tau')
    #print(list.files('./new_data'))
    for(i in 1:length(sigma_sq_vec)){
      for(j in 1:length(phi_vec)){
        for(k in 1:length(tau_vec)){
          filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_sq_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', sparse, '_', type, '.csv'), collapse = '')
          #print(!(filename %in% list.files('./new_data')))
          if(!(filename %in% list.files(path))){next}
          df_temp = read.csv(paste0(path, filename))[, names]
          colnames(df_temp) = names_alt
          df_temp = melt(df_temp)
          df_temp$sigma_sq = sigma_sq_vec[i]
          df_temp$phi = round(phi_vec[j]/sqrt(2),1)
          df_temp$tau = tau_vec[k]
          
          data = rbind(data, df_temp)
        }
      }
      
    }
    data = data[-1,]
    data = data[complete.cases(data),]
    data_plt = data %>% group_by(sigma_sq, phi, tau, variable) %>% summarise(value = mean(value))
    colnames(data_plt)[4:5] = c('Method', 'value') 
    data_plt$Method = factor(data_plt$Method, levels = names_alt)
    p_list[[n]] = ggplot(data_plt, aes(x = tau, y = value)) + #geom_hline(yintercept=0.95) +
              geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
              scale_fill_manual(values=group.colors[names_alt]) +
              xlab("tau %") +
              facet_grid(sigma_sq ~ phi, scales = 'free', labeller = label_both) +
  theme(legend.text = element_text(size=20), legend.title = element_text(size=22),
        axis.text=element_text(size=18), axis.title=element_text(size=20),
        strip.text.x = element_text(size = 18), strip.text.y = element_text(size = 18))
  }
}

p_list[[1]] + geom_hline(yintercept=0.95)
ggsave(paste0(func, '_coverage.png'), width = 10, height = 5)
p_list[[2]]
ggsave(paste0(func, '_score.png'), width = 10, height = 5)
#p_list[[3]]
#p_list[[4]]
```

```{r}
require(gridExtra)
resample = 'decor'
func = 'friedman'
#sparse = 'NS'
#resample = 'subsample'
p = 1
date = '20231109'
n = 0
p_list = list()
for(type in c('msft_CI_cov', 'msft_CI_score')){
  for(sparse in c('NS')){
    n = n+1
    sigma_sq_vec = c(1, 5)
    phi_vec = c(1, 3, 6)
    tau_vec = as.character(c(1, 25))
    cols = c('tau', 'Method', 'MISE')
    
    path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
                  '/', date, '/')
    
    names = c('NN', 'NNGLS')
    names_alt =  c('NN-nonspatial', 'NN-GLS')
    
    
    data = data.frame(matrix(ncol = 5))
    colnames(data) = c('variable', 'value', 'sigma_sq', 'phi', 'tau')
    #print(list.files('./new_data'))
    for(i in 1:length(sigma_sq_vec)){
      for(j in 1:length(phi_vec)){
        for(k in 1:length(tau_vec)){
          filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_sq_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', sparse, '_', type, '.csv'), collapse = '')
          #print(!(filename %in% list.files('./new_data')))
          if(!(filename %in% list.files(path))){next}
          df_temp = read.csv(paste0(path, filename))[, names]
          colnames(df_temp) = names_alt
          df_temp = melt(df_temp)
          df_temp$sigma_sq = sigma_sq_vec[i]
          df_temp$phi = round(phi_vec[j]/sqrt(2),1)
          df_temp$tau = tau_vec[k]
          
          data = rbind(data, df_temp)
        }
      }
      
    }
    data = data[-1,]
    data = data[complete.cases(data),]
    data_plt = data %>% group_by(sigma_sq, phi, tau, variable) %>% summarise(value = mean(value))
    colnames(data_plt)[4:5] = c('Method', 'value') 
    data_plt$Method = factor(data_plt$Method, levels = names_alt)
    p_list[[n]] = ggplot(data_plt, aes(x = tau, y = value)) + #geom_hline(yintercept=0.95) +
              geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
              scale_fill_manual(values=group.colors[names_alt]) +
              xlab("tau %") +
              facet_grid(sigma_sq ~ phi, scales = 'free', labeller = label_both) +
  theme(legend.text = element_text(size=20), legend.title = element_text(size=22),
        axis.text=element_text(size=18), axis.title=element_text(size=20),
        strip.text.x = element_text(size = 18), strip.text.y = element_text(size = 18))
  }
}

p_list[[1]] + geom_hline(yintercept=0.95) + ylab('Coverage')
ggsave(paste0(func, '_coverage.png'), width = 10, height = 5)
p_list[[2]] + ylab('Interval score')
ggsave(paste0(func, '_score.png'), width = 10, height = 5)
#p_list[[3]]
#p_list[[4]]
```

```{r}
require(gridExtra)
resample = 'decor'
func = 'friedman'
#sparse = 'NS'
#resample = 'subsample'
p = 1
date = '20231109'
n = 0
p_list = list()
for(type in c('CI_cov', 'CI_score')){
  for(sparse in c('NS')){
    n = n+1
    sigma_vec = c(1, 5)
    phi_vec = c(1, 3, 6)
    tau_vec = as.character(c(1, 25))
    cols = c('tau', 'Method', 'MISE')
    
    path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
                  '/', date, '/')
    
    names = c('NN', 'NNGLS')
    names_alt =  c('NN-nonspatial', 'NN-GLS')
    
    
    data = data.frame(matrix(ncol = 5))
    colnames(data) = c('variable', 'value', 'sigma', 'phi', 'tau')
    #print(list.files('./new_data'))
    for(i in 1:length(sigma_vec)){
      for(j in 1:length(phi_vec)){
        for(k in 1:length(tau_vec)){
          filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', sparse, '_', type, '.csv'), collapse = '')
          #print(!(filename %in% list.files('./new_data')))
          if(!(filename %in% list.files(path))){next}
          df_temp = read.csv(paste0(path, filename))[, names]
          colnames(df_temp) = names_alt
          df_temp = melt(df_temp)
          df_temp$sigma = sigma_vec[i]
          df_temp$phi = round(phi_vec[j]/sqrt(2),1)
          df_temp$tau = tau_vec[k]
          
          data = rbind(data, df_temp)
        }
      }
      
    }
    data = data[-1,]
    data = data[complete.cases(data),]
    data_plt = data %>% group_by(sigma, phi, tau, variable) %>% summarise(value = mean(value))
    colnames(data_plt)[4:5] = c('Method', 'value') 
    p_list[[n]] = ggplot(data_plt, aes(x = tau, y = value)) + #geom_hline(yintercept=0.95) +
              geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
              scale_fill_manual(values=group.colors[names_alt]) +
              xlab("tau %") +
              facet_grid(sigma ~ phi, scales = 'free', labeller = label_both) +
              theme(legend.text = element_text(size=15), legend.title = element_text(size=20),
                    axis.text=element_text(size=12), axis.title=element_text(size=15),
                    strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))
  }
}

p_list[[1]] + geom_hline(yintercept=0.95)
p_list[[2]]
#p_list[[3]]
#p_list[[4]]
```

```{r}
require(gridExtra)
resample = 'decor'
func = 'sin'
#sparse = 'NS'
#resample = 'subsample'
p = 1
date = '20231105'
n = 0
p_list = list()
for(type in c('sym_CI_cov', 'sym_CI_score')){
  for(sparse in c('NS', 'S')){
    n = n+1
    sigma_vec = c(1, 5)
    phi_vec = c(1, 3, 6)
    tau_vec = as.character(c(1, 25))
    cols = c('tau', 'Method', 'MISE')
    
    path = paste0('/Users/zhanwentao/Documents/Abhi/NN/Simulation/CI', 
                  '/', date, '/')
    
    names = c('NN', 'NNGLS')
    names_alt =  c('NN', 'NNGLS')
    
    
    data = data.frame(matrix(ncol = 5))
    colnames(data) = c('variable', 'value', 'sigma', 'phi', 'tau')
    #print(list.files('./new_data'))
    for(i in 1:length(sigma_vec)){
      for(j in 1:length(phi_vec)){
        for(k in 1:length(tau_vec)){
          filename = paste0(c(func, 'phi', phi_vec[j], 'sig', sigma_vec[i], 'tau', tau_vec[k], 'mtd_', resample, '_', sparse, '_', type, '.csv'), collapse = '')
          #print(!(filename %in% list.files('./new_data')))
          if(!(filename %in% list.files(path))){next}
          df_temp = read.csv(paste0(path, filename))[, names]
          colnames(df_temp) = names_alt
          df_temp = melt(df_temp)
          df_temp$sigma = sigma_vec[i]
          df_temp$phi = round(phi_vec[j]/sqrt(2),1)
          df_temp$tau = tau_vec[k]
          
          data = rbind(data, df_temp)
        }
      }
      
    }
    data = data[-1,]
    data = data[complete.cases(data),]
    data_plt = data %>% group_by(sigma, phi, tau, variable) %>% summarise(value = mean(value))
    colnames(data_plt)[4:5] = c('Method', 'value') 
    p_list[[n]] = ggplot(data_plt, aes(x = tau, y = value)) + geom_hline(yintercept=0.95) +
              geom_bar(aes(fill = Method), position = "dodge", stat="identity") + 
              #scale_fill_manual(values=group.colors[names_alt]) +
              xlab("tau %") +
              facet_grid(sigma ~ phi, scales = 'free', labeller = label_both) +
              theme(legend.text = element_text(size=15), legend.title = element_text(size=20),
                    axis.text=element_text(size=12), axis.title=element_text(size=15),
                    strip.text.x = element_text(size = 10), strip.text.y = element_text(size = 10))
  }
}

p_list[[1]]
p_list[[2]]
p_list[[3]]
p_list[[4]]
```



